Total Amount of Vaccinations by Age Among Black population in the Target Zip Codes

### 2023-04-06 code/analysis_code/analysiscode3.qmd
Part 4

# Total Amount of vaccinations by gender among Black population in the target zip codes

@@

### Dropping all variables except for black males and black females within 31701

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

@@

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31701_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31701_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31701_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31701_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31701_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31701_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31701_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31701_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31701_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31701_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31701_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31701_total_black$total_fblack_vax_Feb_26) 
```

#Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February #Total contains the vaccination totals for each month

```{r}
Gender_Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Male_Total = c(3371, 3358, 3368, 3379, 3387, 3397),
                          Female_Total = c(4426, 4422, 4387, 4394, 4405, 4420))
```

### Converting the Gender_Sum_by_month_31701 to long data in order to plot
```{r}
Gender_Sum_by_month_31701_long = reshape2::melt(Gender_Sum_by_month_31701, id = "Date")
```

### Changing "variable" to "Gender" and "value" to "Vaccination_total"

```{r}
Gender_Sum_by_month_31701_long <- Gender_Sum_by_month_31701_long %>% 
  rename("Gender" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by gender in the 31701 zip code

```{r}
plot_Gender_black_vax = Gender_Sum_by_month_31701_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31701") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax
```

@@

```{r}
plotly_plot_Gender_black_vax = ggplotly(plot_Gender_black_vax)
plotly_plot_Gender_black_vax
```

## Zip code: 31705

@@

### Dropping all variables except for black males and black females within 31705

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31705_total_black = processed_combined_31705 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31705_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31705_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31705_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31705_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31705_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31705_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31705_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31705_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31705_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31705_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31705_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31705_total_black$total_fblack_vax_Feb_26) 
```

#Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February #Total contains the vaccination totals for each month

```{r}
Gender_Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Male_Total = c(4394, 4397, 4399, 4391, 4403, 4399),
                          Female_Total = c(5989, 5930, 5904, 5910, 5934, 5949))
```

### Converting the Gender_Sum_by_month_31705 to long data in order to plot
```{r}
Gender_Sum_by_month_31705_long = reshape2::melt(Gender_Sum_by_month_31705, id = "Date")
```

### Changing "variable" to "Gender" and "value" to "Vaccination_total"

```{r}
Gender_Sum_by_month_31705_long <- Gender_Sum_by_month_31705_long %>% 
  rename("Gender" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by gender in the 31705 zip code

```{r}
plot_Gender_black_vax_31705 = Gender_Sum_by_month_31705_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31705") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31705
```

@@

```{r}
plotly_plot_Gender_black_vax_31705 = ggplotly(plot_Gender_black_vax_31705)
plotly_plot_Gender_black_vax_31705
```

@@

### Dropping all variables except for black males and black females within 31707

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

```{r}
processed_combined_31707_total_black = processed_combined_31707 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_31707_total_black$total_mblack_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_mblack_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_mblack_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_mblack_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_mblack_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_31707_total_black$total_fblack_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_fblack_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_fblack_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_fblack_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_fblack_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_fblack_vax_Feb_26) 
```

#Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February #Total contains the vaccination totals for each month

```{r}
Gender_Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Male_Total = c(3698, 3674, 3678, 3680, 3684, 3681),
                          Female_Total = c(5337, 5311, 5319, 5325, 5351, 5361))
```

### Converting the Gender_Sum_by_month_31707 to long data in order to plot
```{r}
Gender_Sum_by_month_31707_long = reshape2::melt(Gender_Sum_by_month_31707, id = "Date")
```

### Changing "variable" to "Gender" and "value" to "Vaccination_total"

```{r}
Gender_Sum_by_month_31707_long <- Gender_Sum_by_month_31707_long %>% 
  rename("Gender" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by gender in the 31707 zip code

```{r}
plot_Gender_black_vax_31707 = Gender_Sum_by_month_31707_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 31707") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax_31707
```

@@

```{r}
plotly_plot_Gender_black_vax_31707 = ggplotly(plot_Gender_black_vax_31707)
plotly_plot_Gender_black_vax_31707
```

>>>>

# Total Amount of vaccinations by Age among Black population in the target zip codes

@@

### Dropping all variables except for black age groups within 31701

#### Using the select() function to subset the data frame by columns that start with an age group

@@

### Summing each Month variable by age group by month
```{r}
#Summing for ages 5-9 by month 
sum(processed_combined_31701_Age_black$total_05_09_vax_Sept_17) 
sum(processed_combined_31701_Age_black$total_05_09_vax_Oct_28) 
sum(processed_combined_31701_Age_black$total_05_09_vax_Nov_24) 
sum(processed_combined_31701_Age_black$total_05_09_vax_Dec_29) 
sum(processed_combined_31701_Age_black$total_05_09_vax_Jan_26) 
sum(processed_combined_31701_Age_black$total_05_09_vax_Feb_26)

#Summing for ages 10-17 by month 
sum(processed_combined_31701_Age_black$total_10_17_vax_Sept_17) 
sum(processed_combined_31701_Age_black$total_10_17_vax_Oct_28) 
sum(processed_combined_31701_Age_black$total_10_17_vax_Nov_24) 
sum(processed_combined_31701_Age_black$total_10_17_vax_Dec_29) 
sum(processed_combined_31701_Age_black$total_10_17_vax_Jan_26) 
sum(processed_combined_31701_Age_black$total_10_17_vax_Feb_26)

#Summing for ages 18-44 by month 
sum(processed_combined_31701_Age_black$total_18_44_vax_Sept_17) 
sum(processed_combined_31701_Age_black$total_18_44_vax_Oct_28) 
sum(processed_combined_31701_Age_black$total_18_44_vax_Nov_24) 
sum(processed_combined_31701_Age_black$total_18_44_vax_Dec_29) 
sum(processed_combined_31701_Age_black$total_18_44_vax_Jan_26) 
sum(processed_combined_31701_Age_black$total_18_44_vax_Feb_26)

#Summing for ages 45-64 by month 
sum(processed_combined_31701_Age_black$total_45_64_vax_Sept_17) 
sum(processed_combined_31701_Age_black$total_45_64_vax_Oct_28) 
sum(processed_combined_31701_Age_black$total_45_64_vax_Nov_24) 
sum(processed_combined_31701_Age_black$total_45_64_vax_Dec_29) 
sum(processed_combined_31701_Age_black$total_45_64_vax_Jan_26) 
sum(processed_combined_31701_Age_black$total_45_64_vax_Feb_26)

#Summing for ages 65+ by month 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Sept_17) 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Oct_28) 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Nov_24) 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Dec_29) 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Jan_26) 
sum(processed_combined_31701_Age_black$total_65Plus_vax_Feb_26)

```

### Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February #Total contains the vaccination totals for each month

```{r}
Age_Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Age_05_09 = c(123, 126, 126, 127, 127, 128),
                          Age_10_17 = c(642, 635, 633, 637, 630, 629),
                          Age_18_44 = c(3310, 3316, 3313, 3323, 3325, 3331),
                          Age_45_64 = c(3229, 3244, 3239, 3259, 3264, 3258),
                          Age_65Plus = c(2576, 2570, 2569, 2574, 2568, 2572))

```

### Converting the Age_Sum_by_month_31701 to long data in order to plot
```{r}
Age_Sum_by_month_31701_long = reshape2::melt(Age_Sum_by_month_31701, id = "Date")
```

### Changing "variable" to "Age" and "value" to "Vaccination_total"

```{r}
Age_Sum_by_month_31701_long <- Age_Sum_by_month_31701_long %>% 
  rename("Age" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by Age in the 31701 zip code

```{r}
plot_Age_black_vax = Age_Sum_by_month_31701_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Age, 
                                color = Age)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Age_black_vax = plot_Age_black_vax + 
  ggtitle("Vaccination Totals for Black population by Age in 31701") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Age_black_vax
```

@@

```{r}
plotly_plot_Age_black_vax = ggplotly(plot_Age_black_vax)
plotly_plot_Age_black_vax
```

------------------------------------------------------------------------
## Zip code: 31705

@@

### Dropping all variables except for black age groups within 31705

#### Using the select() function to subset the data frame by columns that start with an age group

```{r}
processed_combined_31705_Age_black = processed_combined_31705 %>% 
  select(starts_with("total_05_09"), starts_with("total_10_17"), starts_with("total_18_44"), starts_with("total_45_64"), starts_with("total_65Plus"))
```

### Summing each Month variable by age group by month
```{r}
#Summing for ages 5-9 by month 
sum(processed_combined_31705_Age_black$total_05_09_vax_Sept_17) 
sum(processed_combined_31705_Age_black$total_05_09_vax_Oct_28) 
sum(processed_combined_31705_Age_black$total_05_09_vax_Nov_24) 
sum(processed_combined_31705_Age_black$total_05_09_vax_Dec_29) 
sum(processed_combined_31705_Age_black$total_05_09_vax_Jan_26) 
sum(processed_combined_31705_Age_black$total_05_09_vax_Feb_26)

#Summing for ages 10-17 by month 
sum(processed_combined_31705_Age_black$total_10_17_vax_Sept_17) 
sum(processed_combined_31705_Age_black$total_10_17_vax_Oct_28) 
sum(processed_combined_31705_Age_black$total_10_17_vax_Nov_24) 
sum(processed_combined_31705_Age_black$total_10_17_vax_Dec_29) 
sum(processed_combined_31705_Age_black$total_10_17_vax_Jan_26) 
sum(processed_combined_31705_Age_black$total_10_17_vax_Feb_26)

#Summing for ages 18-44 by month 
sum(processed_combined_31705_Age_black$total_18_44_vax_Sept_17) 
sum(processed_combined_31705_Age_black$total_18_44_vax_Oct_28) 
sum(processed_combined_31705_Age_black$total_18_44_vax_Nov_24) 
sum(processed_combined_31705_Age_black$total_18_44_vax_Dec_29) 
sum(processed_combined_31705_Age_black$total_18_44_vax_Jan_26) 
sum(processed_combined_31705_Age_black$total_18_44_vax_Feb_26)

#Summing for ages 45-64 by month 
sum(processed_combined_31705_Age_black$total_45_64_vax_Sept_17) 
sum(processed_combined_31705_Age_black$total_45_64_vax_Oct_28) 
sum(processed_combined_31705_Age_black$total_45_64_vax_Nov_24) 
sum(processed_combined_31705_Age_black$total_45_64_vax_Dec_29) 
sum(processed_combined_31705_Age_black$total_45_64_vax_Jan_26) 
sum(processed_combined_31705_Age_black$total_45_64_vax_Feb_26)

#Summing for ages 65+ by month 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Sept_17) 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Oct_28) 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Nov_24) 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Dec_29) 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Jan_26) 
sum(processed_combined_31705_Age_black$total_65Plus_vax_Feb_26)

```

### Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February 
### Total contains the vaccination totals for each month

```{r}
Age_Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Age_05_09 = c(210, 211, 209, 201, 202, 202),
                          Age_10_17 = c(1159, 1171, 1169, 1163, 1168, 1167),
                          Age_18_44 = c(5201, 5215, 5239, 5263, 5278, 5281), #pretty notable increase for ages 18-44 
                          Age_45_64 = c(4380, 4381, 4366, 4364, 4367, 4367),
                          Age_65Plus = c(2983, 3000, 2997, 2997, 2994, 2989))

```

### Converting the Age_Sum_by_month_31705 to long data in order to plot
```{r}
Age_Sum_by_month_31705_long = reshape2::melt(Age_Sum_by_month_31705, id = "Date")
```

### Changing "variable" to "Age" and "value" to "Vaccination_total"

```{r}
Age_Sum_by_month_31705_long <- Age_Sum_by_month_31705_long %>% 
  rename("Age" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by Age in the 31705 zip code

```{r}
plot_Age_black_vax = Age_Sum_by_month_31705_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Age, 
                                color = Age)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Age_black_vax = plot_Age_black_vax + 
  ggtitle("Vaccination Totals for Black population by Age in 31705") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Age_black_vax
```

@@

```{r}
plotly_plot_Age_black_vax = ggplotly(plot_Age_black_vax)
plotly_plot_Age_black_vax
```

@@

### Dropping all variables except for black age groups within 31707

#### Using the select() function to subset the data frame by columns that start with an age group

```{r}
processed_combined_31707_Age_black = processed_combined_31707 %>% 
  select(starts_with("total_05_09"), starts_with("total_10_17"), starts_with("total_18_44"), starts_with("total_45_64"), starts_with("total_65Plus"))
```

### Summing each Month variable by age group by month
```{r}
#Summing for ages 5-9 by month 
sum(processed_combined_31707_Age_black$total_05_09_vax_Sept_17) 
sum(processed_combined_31707_Age_black$total_05_09_vax_Oct_28) 
sum(processed_combined_31707_Age_black$total_05_09_vax_Nov_24) 
sum(processed_combined_31707_Age_black$total_05_09_vax_Dec_29) 
sum(processed_combined_31707_Age_black$total_05_09_vax_Jan_26) 
sum(processed_combined_31707_Age_black$total_05_09_vax_Feb_26)

#Summing for ages 10-17 by month 
sum(processed_combined_31707_Age_black$total_10_17_vax_Sept_17) 
sum(processed_combined_31707_Age_black$total_10_17_vax_Oct_28) 
sum(processed_combined_31707_Age_black$total_10_17_vax_Nov_24) 
sum(processed_combined_31707_Age_black$total_10_17_vax_Dec_29) 
sum(processed_combined_31707_Age_black$total_10_17_vax_Jan_26) 
sum(processed_combined_31707_Age_black$total_10_17_vax_Feb_26)

#Summing for ages 18-44 by month 
sum(processed_combined_31707_Age_black$total_18_44_vax_Sept_17) 
sum(processed_combined_31707_Age_black$total_18_44_vax_Oct_28) 
sum(processed_combined_31707_Age_black$total_18_44_vax_Nov_24) 
sum(processed_combined_31707_Age_black$total_18_44_vax_Dec_29) 
sum(processed_combined_31707_Age_black$total_18_44_vax_Jan_26) 
sum(processed_combined_31707_Age_black$total_18_44_vax_Feb_26)

#Summing for ages 45-64 by month 
sum(processed_combined_31707_Age_black$total_45_64_vax_Sept_17) 
sum(processed_combined_31707_Age_black$total_45_64_vax_Oct_28) 
sum(processed_combined_31707_Age_black$total_45_64_vax_Nov_24) 
sum(processed_combined_31707_Age_black$total_45_64_vax_Dec_29) 
sum(processed_combined_31707_Age_black$total_45_64_vax_Jan_26) 
sum(processed_combined_31707_Age_black$total_45_64_vax_Feb_26)

#Summing for ages 65+ by month 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Sept_17) 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Oct_28) 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Nov_24) 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Dec_29) 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Jan_26) 
sum(processed_combined_31707_Age_black$total_65Plus_vax_Feb_26)

```

### Separating sums by month into a data fram consisting of two variables: Date and Total Date contains months September-February 
### Total contains the vaccination totals for each month

```{r}
Age_Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Age_05_09 = c(275, 277, 280, 282, 284, 283),
                          Age_10_17 = c(1109, 1120, 1125, 1134, 1136, 1142),
                          Age_18_44 = c(5903, 5931, 5943, 5947, 5960, 5958),
                          Age_45_64 = c(5130, 5120, 5125, 5123, 5133, 5140),
                          Age_65Plus = c(4200, 4204, 4195, 4206, 4202, 4189))

```

### Converting the Age_Sum_by_month_31707 to long data in order to plot
```{r}
Age_Sum_by_month_31707_long = reshape2::melt(Age_Sum_by_month_31707, id = "Date")
```

### Changing "variable" to "Age" and "value" to "Vaccination_total"

```{r}
Age_Sum_by_month_31707_long <- Age_Sum_by_month_31707_long %>% 
  rename("Age" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by Age in the 31707 zip code

```{r}
plot_Age_black_vax = Age_Sum_by_month_31707_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Age, 
                                color = Age)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Age_black_vax = plot_Age_black_vax + 
  ggtitle("Vaccination Totals for Black population by Age in 31707") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Age_black_vax
```

@@

```{r}
plotly_plot_Age_black_vax = ggplotly(plot_Age_black_vax)
plotly_plot_Age_black_vax
```
